Doing a PhD abroad was one of the biggest challenges of my life, and I would like to acknowledge everyone who helped me to reach this achievement.

First, I thank my advisors, Patricia Stolf and Stephane Caux, for the lessons, patience, and guidance over these three years. You were essential in every part of this work, always reminding me to balance development and research. Also, I want to express my gratitude to Rodrigo Righi, my master's advisor from Brazil, for all the help before the PhD. All these professors made me the researcher that I am today. 

I thank the reviewers, Jesus Carretero and Jean-Marc Menaud, and the jury members, Pierre-François Dutot, Raphael Feraud, and Bruno Sareni. Your suggestions, questions, and scientific exchanges were essential to this work validation. Regarding my work, I would like to express my gratitude to the Agence Nationale de la Recherche (ANR) for funding my PhD as a part of the DATAZERO2 project (ANR-19-CE25-0016).

I would also like to thank all my colleagues from the DATAZERO2 project: Alexis, Amal, Christophe, Emilien, Georges, Jean-Marc Nicod, Jean-Marc Pierson, Jérôme, Laurent, Leila, Louis-Claude, Millian, Robin, and Véronika. All the discussions with you were important for my development and this thesis. To the DATAZERO2's PhD students, Damien, Daniel, Maël, and Manal, I am very grateful for all the moments that we shared, from the work meetings to the fun times.  

For my colleagues and friends made through the LAPLACE laboratory, especially Abdulrahman, Alessandro Poles, Alessandro Oliveira, Andrea, Carole, Corentin, Daouda, Diego, Dov, Dyalla, Erick, Evelise, Fernanda, Gianmarco, Gregory, Joseph, Lorenzo, Luc, Lucas, Maxime, Miguel, Paul, Pawel, Rafael Accacio, Ryan, and Youssef, my eternal gratitude. You helped me to go through all the challenges imposed by a thesis. Without your support, I do not know if I could finish it. 

I also want to express my gratitude to my family for all your support and encouragement during my life and this PhD. It is hard to be away from you, but I was still able to receive your love. I can not forget to thank my Brazilian friends, especially Samuel and Bruno Fernandes. Your funny messages were what I needed in some difficult moments. Finally, I thank my wife, Carla. You supported me since we met. You bring color to my life, and I love you so much. This thesis is not only mine, it is also yours. Thank you for all your love and caring. 